Fitness effects of mutations to SARS-CoV-2 proteins

### 2023-01-15 paper/paper.tex
add `E_heatmap` figure

E protein mutation effects with minimum expected counts of 20 and \textbf{x} marking wildtype identity in Wuhan-Hu-1.

\includegraphics[width=\linewidth, trim={0 0 0 0.4in}, clip=true]{figs/E_view1.pdf}

E protein mutation effects with minimum expected counts of 5 and \textbf{x} marking wildtype identity in BQ.1.

\includegraphics[width=\linewidth, trim={0 0 0 0.4in}, clip=true]{figs/E_view2.pdf}
\caption{
Effects of amino-acid mutations to E protein.
{\bf (A)} and {\bf (B)} provide two views of the estimated mutation effects with different thresholds for the minimum expected counts and different references used to mark the ``wildtype'' identity, as indicated in the titles above the plots.
For both panels, the area plot at top shows the average effects of mutations at each site, and the heatmap shows the effects of specific amino acids.
An interactive version of this plot at \url{https://jbloomlab.github.io/SARS2-mut-fitness/E.html} enables zooming, mouseovers, and exploration of the data.
Comparable interactive plots for all other viral proteins are linked at \jdbcomment{create landing pad page with these links}.
\label{fig:E}
}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{figs/E_heatmap.pdf}
\caption{
Effects of amino-acid mutations to E protein.
The area plot at top shows the average effects of mutations at each site, and the heatmap shows the effects of specific amino acids, with \textbf{x} denoting the amino-acid identity in the Wuhan-Hu-1 strain.
Only mutations with at least 10 expected counts are shown.
See \url{https://jbloomlab.github.io/SARS2-mut-fitness/E.html} for an interactive version of this plot that enables zooming, mouseovers, and adjustment of the minimum expected count threshold.
See the links at \url{https://jbloomlab.github.io/SARS2-mut-fitness} for comparable interactive plots for all other SARS-CoV-2 proteins.
\label{fig:E_heatmap}
}
\end{figure*}
